PMV formulations: which one is the most accurate?

### 2022-06-09 Manuscript/src/myglossary.tex
paper: minor edits

\newglossaryentry{ipm}{
    name={Incremental PM},
    description={Incremental Personal Model}
}

\newglossaryentry{gpm}{
    name={Warm start PM},
    description={Warm start Personal Model}
}

\newglossaryentry{pm}{
    name={PM},
    description={Personal Model}
}
\newglossaryentry{ib}
{
name={iButton\textsuperscript{\tiny\textregistered}},
description={Wireless temperature sensors},
plural={iButtons\textsuperscript{\tiny\textregistered}},
firstplural={iButtons\textsuperscript{\tiny\textregistered}}
}

\newglossaryentry{ubibot}
{
name={UbiBot\textsuperscript{\tiny\textregistered}},
description={Wireless environmental sensor},
}

@@

>>>>

@@

\newglossaryentry{rhrn}
{
name={right-here-right-now},
description={Right here right now thermal comfort survey}
}

\newglossaryentry{pmv-ce}
{
name={PMV\textsubscript{CE}},
description={PMV calculated in accordance with the ASHRAE~55--2020}
}

\newglossaryentry{db2}
{
name={Comfort DB},
description={ASHRAE Global Thermal Comfort Database II}
}

### 2022-06-09 Manuscript/src/sections/introduction.tex
paper: minor edits

% Document

@@

    In 1970, Fanger~\cite{Fanger1970} developed the \ac{pmv} model, which is now incorporated into the \gls{7730} Standard~\cite{iso7730} in its original form.
    The \ac{pmv} is the most extensively used thermal comfort index for estimating the thermal sensation of a group of people sharing the same thermal environment.
    It is used both by researchers and practitioners.
    However, Cheung et al. (2019) demonstrated that the accuracy of the \ac{pmv} in predicting self-reported thermal sensation of people is only \qty{34}{\percent}~\cite{Cheung2019}.

    ASHRAE 55:2020 Standard utilizes a modified version of the PMV model [4] that calculates a Cooling Effect (CE) using the Standard Effective Temperature (SET) equation for air speeds higher than \qty{0.1}{\m\per\s}.
    The value of CE is then subtracted from both the measured dry-bulb air temperature (tdb) and \ac{tr} and these results become the input into the PMV model.
    Since the CE already accounts for convective heat losses from the person to the environment, the air speed used to calculate the PMV value is set to 0.1 m/s.

>>>>

@@

    In 1970, Fanger~\cite{Fanger1970} developed the \ac{pmv} model, which is now incorporated into the \gls{7730} Standard~\cite{iso7730} in its original form.
    The \ac{pmv} model has been widely adopted worldwide both among researchers and practitioners.
    The \ac{pmv} is the most extensively used thermal comfort index for estimating the thermal sensation of a group of people sharing the same thermal environment.
    However, Cheung et al. (2019) demonstrated that the accuracy of the \ac{pmv} in predicting self-reported thermal sensation of people is only \qty{34}{\percent}~\cite{Cheung2019}.

    To overcome this problem, the \gls{55} Standard introduced a modified version of the \ac{pmv}, the \gls{pmv-ce}~\cite{ashrae552020}.
    For \ac{v} higher than \qty{0.1}{\m\per\s} the \gls{55} prescribes the use of the \ac{ce}.
    The value of \ac{ce}, calculated using the \ac{set} equation, is subtracted from both the value of \ac{tdb} and \ac{tr} and these results become the input into the \ac{pmv} model.
    The \ac{ce} already accounts for convective heat losses from the person to the environment, thus, the value of \ac{v}, used to calculate the \ac{pmv}, is set to \qty{0.1}{\m\per\s}.
    The other three input parameters (\ac{clo}, \ac{met}, and \ac{rh}) are not modified.
    Consequently, given the same thermal environment and same occupants, results from the two \ac{pmv} formulation differ when the value of \ac{v} is higher than \qty{0.1}{\m\per\s}.
    This may be a source of confusion for many users worldwide since both the \gls{7730} and the \gls{55} are the widely adopted and incorporated in many national building codes worldwide.
    In addition, over the course of the last \num{50} years, other formulations of the \ac{pmv} model have been formulated by other researchers.
    To our knowledge, no other study compared the accuracy all the aforementioned  two aforementioned PMV models.
    One study compared the accuracy of the \ac{pmv-ce} and the \ac{pmv} model.

    This study aims to specifically fill this knowledge gap by comparing the results of the \ac{pmv} formulations developed over the course of the last years with self-reported \ac{tsv} contained in the ASHRAE Global Thermal Comfort Database II v2.1, referred to as the \gls{db2} thereafter.

### 2022-06-09 Manuscript/src/sections/titleAbstract.tex
paper: minor edits

    \title{Title of the paper}

@@

    \begin{abstract}
        The \ac{pmv} model developed by Fanger predicts thermal sensation.
    %    It is used in its original formulation in the \gls{iso}, while the \gls{ashrae} uses a modified version \acs{pmv-ce} to better account for air speeds.
        We compared their results against XXX thermal sensation votes collected in buildings.
    \end{abstract}

>>>>

    \title{PMV formulations: which one is the most accurate?}

@@

    \begin{abstract}
        The \ac{pmv} model was originally developed by Fanger to predict the thermal sensation of a large group of occupants sharing the same thermal environment.
        His model has seen widespread adoption and it is currently used in the \gls{7730}.
        However, to compensate for the model low prediction accuracy several other formulations have been proposed, one of which is currently used in the \gls{55}.
        This is a source of confusion for many practitioners and researchers who find it difficult to settle on which formulation they should use.
        We aim to solve this problem by comparing the accuracy of the main \ac{pmv} formulations against \var{tot_surveys} thermal sensation votes collected in buildings.
        % We found that for V>0.1m/s the \gls{pmv-ce} is significantly more accurate (48%) than the PMV (42%) in predicting thermal neutrality.
        % In 95% of the cases, the error was less than one point.
        % The PMV and PMVCE accuracy were 35% and 36% for |PMV|≤2 and 43% and 44% for |PMV|≤1, respectively.
        % Neither PMV model could accurately predict ‘cold’, ‘cool’, ‘warm’, or ‘hot’ thermal sensations.
        % Consequently, the PMV should only be used in conditions close to neutrality within the range |PMV|≤1.
        % We open-sourced the source code.
    \end{abstract}
